---
title: "Homework 5"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(p8105.datasets)
library(viridis)
library(purrr)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

# Problem 1

waiting for solution release .. hopefully ...

# Problem 2

```{r}
library(rvest)
```

Create a tidy dataframe

```{r}
names_df =
  tibble(
    files = list.files("data/"),
    path = str_c("data/", files)) |> 
  mutate(data = map(path, read_csv)) |> 
  unnest()

p2_df =
  names_df |> 
  mutate(
    files = str_replace(files, ".csv", ""),
    arm = str_sub(files, 1, 3),
    ID = str_sub(files, 5, 7)) |> 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    values_to = "observation",
    names_prefix = "week_") |> 
  mutate(week = as.numeric(week)) |> 
  select(arm, ID, week, observation)
```

Create a spaghetti plot showing observations on each subject over time and comment

```{r}
p2_df |> 
  ggplot(aes(x = week, y = observation, color = ID)) +
  geom_line() +
  facet_wrap(~arm) +
  labs(x = "Week", y = "Observations", title = "Observations on Subjects over Time")
```

There was no marked increase or decrease in observation values for the participants in the control arm. The majority of the values in the control arm stayed between observation values -1.25 and 3.75. The values in the experimental arm, however, generally increased over the course of the 8 weeks. The values generally started at week 0 in the range of -1.25 to 3.75, but by week 8, the values fell within the range of 2.5 to 7.5.

# Problem 3

Set elements, generate datasets

```{r}
sim_mean = function(mu) {
  data = tibble(
    x = rnorm(n=30, mean = mu, sd = 5),
  )
output = data |>
  t.test() |>
  broom::tidy() |>
  select(estimate, p.value) |>
  rename(mu_hat=estimate, pval=p.value)
}
```

Repeat for mu = 1, 2, 3, 4, 5, 6
```{r}
sim_results = expand_grid(
  mu_df = c(0, 1, 2, 3, 4, 5, 6),
  iter = 1:5000
) |>
  mutate(
    estimate = map(mu_df, sim_mean)
  ) |>
  unnest(estimate)
```

Plot showing proportion of times null was rejected and true value of mu

```{r}
sim_results |>
  group_by(mu_df) |> 
  summarise(
    reject = sum(pval < 0.05),
    proport = reject/5000) |> 
  ggplot(aes(x = mu_df, y = proport)) +
  geom_point() +
  geom_line() +
  labs(x = "True value of μ", y = "Power", title = "Power of the test and the true value of μ")
```

The plot depicts a curve of test power that increases between the true values of mu of 0 to around 4 until it plateaus. The plot indicates that as the effect size increases, the power of the test also increases.


