---
title: "Homework 5"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(p8105.datasets)
library(viridis)
library(purrr)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

# Problem 1

waiting for solution release .. hopefully ...

# Problem 2

```{r}
library(rvest)
```

Create a tidy dataframe

```{r}
names_df =
  tibble(
    files = list.files("data/"),
    path = str_c("data/", files)) |> 
  mutate(data = map(path, read_csv)) |> 
  unnest()

p2_df =
  names_df |> 
  mutate(
    files = str_replace(files, ".csv", ""),
    arm = str_sub(files, 1, 3),
    ID = str_sub(files, 5, 7)) |> 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    values_to = "observation",
    names_prefix = "week_") |> 
  mutate(week = as.numeric(week)) |> 
  select(arm, ID, week, observation)
```

Create a spaghetti plot showing observations on each subject over time and comment

```{r}
p2_df |> 
  ggplot(aes(x = week, y = observation, color = ID)) +
  geom_line() +
  facet_wrap(~arm) +
  labs(x = "Week", y = "Observations", title = "Observations on Subjects over Time")
```

There was no marked increase or decrease in observation values for the participants in the control arm. The majority of the values in the control arm stayed between observation values -1.25 and 3.75. The values in the experimental arm, however, generally increased over the course of the 8 weeks. The values generally started at week 0 in the range of -1.25 to 3.75, but by week 8, the values fell within the range of 2.5 to 7.5.


